\chapter{Technologies Used}

\section{Overview}

The \textbf{PrepSmart platform} is developed using a modern and efficient technology stack that ensures scalability, performance, and ease of development. The system follows a \textbf{full-stack web development approach,} where the frontend, backend, and database are designed as independent yet interconnected components.

\vspace{0.2cm}

The frontend is responsible for delivering an interactive and responsive user interface, while the backend handles business logic, API communication, and data processing. The database is used for persistent storage of application data such as user information, test results, and analytics.

\vspace{0.2cm}

The selected technologies were chosen based on their \textbf{performance, flexibility, community support, and compatibility} with real-world application development.

\section{Frontend Technologies}

The frontend of the \textbf{PrepSmart platform} is developed using React, a popular JavaScript library for building user interfaces. \textbf{React} enables the creation of dynamic and reusable UI components, improving development efficiency and maintainability. Additional frontend technologies include:

\begin{itemize}[noitemsep, topsep=2pt]
    \item \textbf{HTML (HyperText Markup Language):} Used for structuring web content.
    \item \textbf{CSS (Cascading Style Sheets):} Used for styling and layout design.
    \item \textbf{JavaScript (JS):} Provides interactivity and dynamic behavior.
    \item \textbf{Axios / Fetch API:} Used for making HTTP requests to the backend.
\end{itemize}

React’s component-based architecture allows efficient state management and improves user experience by enabling fast rendering and seamless navigation across the platform.

\section{Backend Technologies}

The backend of the PrepSmart platform is developed using \textbf{Django REST Framework (DRF)}, which is a powerful toolkit for building Web APIs in Python. Key backend technologies include:

\begin{itemize}[noitemsep, topsep=2pt]
    \item \textbf{Django:} A high-level Python web framework that promotes rapid development and clean design.
    \item \textbf{Django REST Framework (DRF):} Used to create RESTful APIs for communication between frontend and backend.
    \item \textbf{JWT (JSON Web Token):} Used for secure user authentication and authorization.
\end{itemize}

\section{Database}

The platform uses \textbf{MySQL}, a relational database management system, for storing structured data efficiently. The database stores:

\begin{itemize}[noitemsep, topsep=2pt]
    \item User information and profiles
    \item Learning progress and tracks
    \item Practice questions and test data
    \item Analytics and performance metrics
\end{itemize}

MySQL ensures data consistency, reliability, and supports complex queries required for analytics and reporting.

\section{Other Tools And Technologies}

The development and execution of the PrepSmart platform also involve additional tools and technologies:

\begin{itemize}[noitemsep, topsep=2pt]
    \item \textbf{Python:} Used for backend logic and code execution.
    \item \textbf{Local Code Execution Engine:} Allows users to run Python code in real-time.
    \item \textbf{VS Code:} Used as the primary development environment.
    \item \textbf{Git \& GitHub:} Used for version control and project management.
    \item \textbf{Postman:} Used for API testing and debugging.
\end{itemize}

These tools enhance development efficiency, debugging, and deployment readiness of the system.

\begin{table}[H]
    \centering
    \caption{Technology Stack Overview}
    \label{tab:tech_stack}
    
    \renewcommand{\arraystretch}{1.4} % increases row height
    \setlength{\tabcolsep}{10pt} % increases column spacing
    
    \begin{tabular}{|p{4cm}|p{8cm}|}
        \hline
        \textbf{Layer} & \textbf{Technology Used} \\ \hline
        Frontend & React, HTML, CSS, JavaScript \\ \hline
        Backend & Django, Django REST Framework \\ \hline
        Database & MySQL \\ \hline
        Authentication & JSON Web Token (JWT) \\ \hline
        Programming Language & Python \\ \hline
        Tools & GitHub, Postman, VS Code \\ \hline
    \end{tabular}
\end{table}

\newpage