\chapter{Results And Discussion}

\section{Results}

The results of the PrepSmart platform demonstrate the successful implementation of all major modules, providing an integrated and efficient placement preparation system.

\vspace{0.2cm}

The authentication module (refer to Figures 4.1 and 4.2) successfully enables secure user registration and login using JSON Web Tokens (JWT). It ensures safe access control and session management.

\vspace{0.2cm}

The dashboard module (refer to Figures 4.3 and 4.4) provides a comprehensive overview of user performance, including placement readiness, problems solved, accuracy, and daily activities. The dynamic updates confirm proper backend integration and real-time data handling.

\vspace{0.2cm}

The learning path module (refer to Figures 4.5 and 4.6) effectively organizes topics into structured tracks with progress indicators. This validates the system’s ability to guide users through a systematic preparation process.

\vspace{0.2cm}

The practice module (refer to Figures 4.7 and 4.8) successfully delivers topic-wise questions and tracks user performance, including accuracy and progress. It demonstrates effective categorization and recommendation logic.

\vspace{0.2cm}

The mock test module (refer to Figures 4.9, 4.10, and 4.11) simulates real test environments with timed assessments and automatic evaluation. The system accurately calculates scores and maintains test history, ensuring realistic exam simulation.

\vspace{0.2cm}

The code editor module (refer to Figure 4.12) enables real-time Python code execution. The backend correctly processes user code and returns outputs, execution time, and error handling, confirming proper functionality.

\vspace{0.2cm}

The AI interview module (refer to Figures 4.13 and 4.14) presents interview questions and allows users to submit responses. This demonstrates the system’s capability to simulate interview scenarios.

\vspace{0.2cm}

The analytics module (refer to Figure 4.15) provides detailed insights into performance through graphs, weak topic identification, and progress tracking. This confirms the effectiveness of backend-driven analytics.

\section{Discussion}

The overall performance of the PrepSmart platform indicates that the system operates efficiently and meets its intended objectives.

\vspace{0.2cm}

The integration of multiple modules into a single platform eliminates the need for using separate tools, thereby improving user convenience and consistency in preparation. The backend successfully handles API requests and ensures smooth communication between frontend and database.

\vspace{0.2cm}

The dashboard and analytics modules provide meaningful insights, enabling users to identify weak areas and improve their preparation strategy. The visualization of data through graphs enhances user understanding.

\vspace{0.2cm}

The mock test module effectively replicates real exam conditions, helping users develop time management skills. The automatic evaluation system ensures accurate and instant feedback.

\vspace{0.2cm}

The code execution module performs reliably, executing Python code with correct outputs and minimal delay. This validates the efficiency of backend processing.

\vspace{0.2cm}

The AI interview module adds significant value by simulating real-world interview scenarios, helping users improve communication and confidence.

\vspace{0.2cm}

Overall, the system demonstrates strong performance in terms of functionality, usability, and scalability. It successfully transforms placement preparation into a structured, data-driven, and interactive process.

\newpage