\thispagestyle{plain}

\begin{center}
{\Large\bfseries\uppercase{Abstract}}
\end{center}

\vspace{0.4cm}

\justify

\textbf{PrepSmart: Design and Development of a Smart Placement Preparation Platform} is a web-based application developed to provide a unified and structured environment for campus placement preparation. Students often depend on multiple independent platforms for learning, coding practice, mock tests, interview preparation, and progress tracking, resulting in fragmented learning and inefficient preparation. PrepSmart addresses this challenge by integrating these activities into a single platform that supports systematic and personalized learning.

\vspace{0.3cm}

The platform provides structured learning paths, coding practice, mock tests, AI-assisted interview preparation, company-specific preparation, resume and portfolio management, and performance analytics. These modules enable students to monitor their learning progress, identify weak areas, and prepare effectively for technical interviews and campus recruitment.

\vspace{0.3cm}

The system is implemented using \textbf{React} for the frontend, \textbf{Django} and \textbf{Django REST Framework (DRF)} for the backend, and \textbf{MySQL} as the database. Secure authentication is achieved using \textbf{JSON Web Tokens (JWT)}, while RESTful APIs enable efficient communication between the frontend and backend. The platform also includes an integrated coding workspace with code execution and evaluation support.

\vspace{0.3cm}

PrepSmart follows a modular and scalable architecture that simplifies maintenance and supports future enhancements such as adaptive learning recommendations, advanced AI-driven mentoring, and cloud deployment. By combining learning, assessment, coding practice, interview preparation, and analytics within a unified system, the platform enhances learning efficiency, improves placement readiness, and provides students with a comprehensive solution for campus recruitment preparation.

\vspace{0.4cm}

\noindent\textbf{Keywords:} Placement Preparation, React, Django, Django REST Framework, MySQL, JWT Authentication, REST API, Educational Technology.

\newpage