\thispagestyle{plain}

\begin{center}
{\Large\bfseries\uppercase{Acknowledgements}}
\end{center}

\vspace{0.8cm}

I would like to express my sincere gratitude to everyone who contributed to the successful completion of this internship and the preparation of this report.

\vspace{0.2cm}

I would like to express my heartfelt thanks to my Internship Mentor (External Supervisor), \textbf{Akhilesh Reddy Karra}, Architect - Application, and \textbf{Harathi Jayampu}, Jr. Project Manager, at \textbf{AuroPro Soft Systems Pvt Ltd}, for their invaluable guidance, continuous support, and insightful suggestions throughout the development of this project. Their practical insights and industry perspective greatly contributed to shaping this work.

\vspace{0.2cm}

I am equally grateful to my Faculty Supervisor, \textbf{Dr. Kaustubh Dhondge}, Associate Dean (Academics), for his constant encouragement, academic guidance, and support during the course of this project. His mentorship played a crucial role in the successful completion of this work.

\vspace{0.2cm}

I would also like to thank my Faculty Examiner, \textbf{Dr. Reema Patel}, Assistant Professor, for her valuable feedback and suggestions, which helped in improving the quality of this project.

\vspace{0.2cm}

I would like to extend my sincere thanks to \textbf{Polukanti Ravi Kumar} and \textbf{Chitukuru Nalini} for their continuous support and encouragement throughout this journey. Their motivation played an important role in the successful completion of this work.

\vspace{0.2cm}

I also thank the faculty and staff of the \textbf{Department of Computer Science and Engineering, Indian Institute of Information Technology Surat}, for providing me with the academic foundation to pursue this project.

\vspace{0.2cm}

I would also like to express my sincere gratitude to the \textbf{Director, Indian Institute of Information Technology Surat}, for the institutional support and for fostering an environment that encourages students to undertake impactful industry internships.

\vspace{1.5cm}

\begin{flushright}
\textbf{\myname}\\[4pt]
Roll No.: \myrollno \\[4pt]
B.Tech.\ IV Year, CSE\\[4pt]
IIIT Surat, May 2026
\end{flushright}

\newpage