\begin{thebibliography}{99}

\bibitem{react}
Meta Platforms Inc., \emph{React Documentation}. [Online]. Available: \url{https://react.dev/}. Accessed: July 2026.

\bibitem{django}
Django Software Foundation, \emph{Django Documentation}. [Online]. Available: \url{https://docs.djangoproject.com/}. Accessed: July 2026.

\bibitem{drf}
Django REST Framework, \emph{Django REST Framework Documentation}. [Online]. Available: \url{https://www.django-rest-framework.org/}. Accessed: July 2026.

\bibitem{python}
Python Software Foundation, \emph{Python Documentation}. [Online]. Available: \url{https://docs.python.org/3/}. Accessed: July 2026.

\bibitem{mysql}
Oracle Corporation, \emph{MySQL Reference Manual}. [Online]. Available: \url{https://dev.mysql.com/doc/}. Accessed: July 2026.

\bibitem{jwt}
Auth0, \emph{JSON Web Token (JWT) Introduction}. [Online]. Available: \url{https://jwt.io/introduction/}. Accessed: July 2026.

\bibitem{htmlcssjs}
MDN Web Docs, \emph{HTML, CSS and JavaScript Documentation}. [Online]. Available: \url{https://developer.mozilla.org/}. Accessed: July 2026.

\bibitem{postman}
Postman Inc., \emph{Postman Learning Center}. [Online]. Available: \url{https://learning.postman.com/}. Accessed: July 2026.

\bibitem{git}
Git Development Team, \emph{Git Documentation}. [Online]. Available: \url{https://git-scm.com/doc}. Accessed: July 2026.

\bibitem{vscode}
Microsoft Corporation, \emph{Visual Studio Code Documentation}. [Online]. Available: \url{https://code.visualstudio.com/docs}. Accessed: July 2026.

\bibitem{vite}
VoidZero Inc., \emph{Vite Documentation}. [Online]. Available: \url{https://vite.dev/}. Accessed: July 2026.

\bibitem{github}
Mala Neeraj Srinivas, \emph{PrepSmart: Smart Placement Preparation Platform}, GitHub Repository. [Online]. Available: \url{https://github.com/neeraj-cseh/smart-placement-platform}. Accessed: July 2026.

\bibitem{stackoverflow}
Stack Overflow, \emph{Developer Community}. [Online]. Available: \url{https://stackoverflow.com/}. Accessed: July 2026.

\bibitem{chatgpt}
OpenAI, \emph{ChatGPT}. [Online]. Available: \url{https://chatgpt.com/}. Accessed: July 2026.

\bibitem{gemini}
Google DeepMind, \emph{Gemini}. [Online]. Available: \url{https://gemini.google.com/}. Accessed: July 2026.

\bibitem{claude}
Anthropic, \emph{Claude AI}. [Online]. Available: \url{https://claude.ai/}. Accessed: July 2026.

\bibitem{youtube}
YouTube, \emph{Educational Programming and Software Development Tutorials}. [Online]. Available: \url{https://www.youtube.com/}. Accessed: July 2026.

\bibitem{sommerville}
Ian Sommerville, \emph{Software Engineering}, 10th ed. Pearson Education, 2016.

\bibitem{dbmsbook}
Abraham Silberschatz, Henry F. Korth, and S. Sudarshan, \emph{Database System Concepts}, 7th ed. McGraw-Hill, 2019.

\bibitem{uml}
Grady Booch, James Rumbaugh, and Ivar Jacobson, \emph{The Unified Modeling Language User Guide}, 2nd ed. Addison-Wesley, 2005.

\end{thebibliography}